Hierarchical Dispatching and Overriding

### 2017-10-09 NewVersion/paper.tex
Introduction
added page number
Abstract and Intro

\documentclass{llncs}

@@

This paper presents a new model called \emph{\textbf{F}eatherweight
  \textbf{H}ierarchical \textbf{J}ava} (\name{}) that deals with
unintentional method conflicts.
In our
new model, conflicting methods arising from unrelated methods can
coexist in the same component. Furthermore our model supports
\emph{hierarchical method overriding}: that is, methods can be
\emph{independently overridden} along the multiple inheritance
hierarchy. To avoid ambiguity, hierarchical information is 
employed in method dispatching, which uses a combination of static and
dynamic type information to choose the implementation of a method at
run-time. We give illustrative examples of our language and features
and formalize \name{} as a minimal Featherweight-Java style calculus.

>>>>

\documentclass{llncs}
\pagestyle{plain}

@@

This paper presents a new model called \emph{\textbf{F}eatherweight
  \textbf{H}ierarchical \textbf{J}ava} (\name{}) that deals with
unintentional method conflicts.  In our new model, which is partly
inspired by C++, conflicting methods arising from unrelated methods
can coexist in the same class, and \emph{hierarchical dispatching}
supports unambigous lookups in the presence of such conflicting
methods.  To avoid ambiguity, hierarchical information is employed in
method dispatching, which uses a combination of static and dynamic
type information to choose the implementation of a method at run-time.
Furthermore, unlike all existing inheritance models, our model
supports \emph{hierarchical method overriding}: that is, methods can
be \emph{independently overridden} along the multiple inheritance
hierarchy. We give illustrative examples of our language and features
and formalize \name{} as a minimal Featherweight-Java style calculus.

### 2017-10-09 NewVersion/sections/Introduction.tex
Abstract and Intro

C++ and C\# do allow for two
unintentionally conflicting methods to coexist in a class. 
C++ accepts the triangle inheritance and
resolves the ambiguity by \emph{static dispatching} or casts. But the
drawback is that these conflicting methods cannot be further overriden. 
\bruno{how about C\#? Say something about C\# here.}
% However, C++ has
% limited support for virtual methods with unintentional conflicts, and
% it will often throw errors when composing them. This is again
% unsatisfactory because virtual methods are pervasive in OOP and used 
% for code reuse and extensibility. A problem with the C++ approach is
% that programmers can only use either static or dynamic dispatching separately, but dealing
% with unintentional method conflicts seems to require a combination of
% both. 
Some other workarounds or approaches include delegation and
renaming/exclusion in the trait model. However renaming/exclusion 
can break the subtyping relation between a subclass and its parent.
This is not adequate for the class model commonly used in mainstream 
OOP languages, where the subclass is always expected to be a subtype 
of the parent class.

@@

In summary, our contributions are:
\begin{itemize}
	\item \textbf{Hierarchical dispatch algorithm:} an algorithm that integrates both the static type and dynamic type for method dispatch, and hence
	ensures unambiguity as well as extensibility.
	\item \textbf{Hierarchical overriding:} a novel notion that allows
          methods to override on individual branches of the class hierarchy.
	\item \textbf{\name:} a formalized model based on
          Featherweight Java, supporting the above features. 
          We provide the static and dynamic semantics, and prove the
          type soundness of the model.
	\item \textbf{Prototype implementation\footnote{Available in
              supplementary material attached to the submission.}:} a
          simple implementation of \MIM{} implemented in Scala.
          \bruno{Are the examples in the paper implemented in the interpreter?}
          \yanlin{new formalization has not been implemented yet.}
\end{itemize}

>>>>

C++ and C\# do allow for two
unintentionally conflicting methods to coexist in a class. C\# allows
this by interface multiple inheritance and explicit method
implementations. But since C\# is a single inheritance language, 
it is only possible to \emph{implement} multiple interfaces (but not
multiple classes). %We will have more detailed discussion on this in Section~\ref{sec:relatedwork}.
C++ accepts triangle inheritance and
resolves the ambiguity by specifying the expected path by
\emph{upcasts}. However
neither the C\# or C++ approaches allow
such conflicting methods to be further overriden. 
% However, C++ has
% limited support for virtual methods with unintentional conflicts, and
% it will often throw errors when composing them. This is again
% unsatisfactory because virtual methods are pervasive in OOP and used 
% for code reuse and extensibility. A problem with the C++ approach is
% that programmers can only use either static or dynamic dispatching separately, but dealing
% with unintentional method conflicts seems to require a combination of
% both. 
Some other workarounds or approaches include delegation and
renaming/exclusion in the trait model. However renaming/exclusion 
can break the subtyping relation between a subclass and its parent.
This is not adequate for the class model commonly used in mainstream 
OOP languages, where the subclass is always expected to be a subtype 
of the parent class.

@@

In summary, our contributions are:
\begin{itemize}
	\item \textbf{Formalization of a hierarchical dispatching algorithm} that integrates both the static type and dynamic type for method dispatch, and hence
	ensures unambiguity as well as extensibility in the presence
        of unintentional method conflicts.
	\item \textbf{Hierarchical overriding:} a novel notion that allows
          methods to override on individual branches of the class hierarchy.
	\item \textbf{\name:} a formalized model based on
          Featherweight Java, supporting the above features. 
          We provide the static and dynamic semantics, and prove the
          type soundness of the model.
	\item \textbf{Prototype implementation\footnote{Available in
              supplementary material attached to the submission.}:} a
          simple implementation of \MIM{} implemented in Scala.
          \bruno{Are the examples in the paper implemented in the interpreter?}
          \yanlin{new formalization has not been implemented yet.}
\end{itemize}
